---
title: "R Notebook"
output: html_notebook
---


```{r}
library(pollster)
library(survey)
library(haven)
```



```{r}
nfhs5_hhmember=read_dta("/media/abhinav/Datahub/Survey/NFHS/NFHS5/HH Member/IAPR7AFL.DTA",col_select = c(1,2,"hv001","hv005","shweight","hv104","hv021","hv022","hv023","hv024","hv025","sh49",67,399:411))
```


Stunting = height-for-age z-score (HAZ) < −2 (severe if < −3)

Wasting = weight-for-height z-score (WHZ) < −2 (severe if < −3)

Underweight = weight-for-age z-score (WAZ) < −2 (severe if < −3)

```{r}

design <- svydesign(
  id = ~hv021,
  strata = ~hv022,
  weights = ~hv005,
  data = df,
)


svymean(~I(hc5 < -200), design, na.rm = TRUE)

df=nfhs5_hhmember %>% filter(hc1<=59 & !is.na(hc5))%>%
  mutate(is_stunted=case_when(hc5 < -300 ~ "severe stunting",
                              hc5 >= -300 & hc5 < -200 ~ "Stunting",
                              hc5 >= -200 ~ "Normal"),
         dummY_india="All India")%>%filter(hc5 > -600 & hc5 < 600)%>%
    crosstab(x = dummY_india, y = is_stunted,weight = design)
```

```{r}



# Example data: one row per child
# sex: 1 = male, 2 = female (zscorer expects this coding)
# age_months: age in months
# weight_kg: weight in kilograms
# height_cm: length/height in centimeters
# measure: "L" for recumbent length (usually <24 months) or "H" for standing height
df <- tibble::tribble(
  ~id, ~sex, ~age_months, ~weight_kg, ~height_cm, ~measure,
   1,     1,        12,       8.0,        75,     "L",
   2,     2,        36,      14.0,        95,     "H",
   3,     1,        24,      10.0,        80,     "H"
)

# Add WHO z-scores to the dataframe using addWGSR
# Note: argument names must match variable names in your data; supply them by name
df_z <- addWGSR(data = nfhs5_hhmember,sex = "hv104",firstPart = "hc2",secondPart = "hc3",index = "wfh")

# The function adds columns such as: waz (weight-for-age Z), haz (length/height-for-age Z), whz (weight-for-height Z)
# (If your version of zscorer uses slightly different names, inspect names(df_z) after running.)
names(df_z)  # inspect

# Classify malnutrition per NFHS (WHO thresholds)
df_classified <- df_z %>%
  mutate(
    stunting = case_when(
      !is.na(haz) & haz < -3 ~ "Severely stunted",
      !is.na(haz) & haz < -2 ~ "Stunted",
      !is.na(haz)            ~ "Normal",
      TRUE                   ~ NA_character_
    ),
    wasting = case_when(
      !is.na(whz) & whz < -3 ~ "Severely wasted",
      !is.na(whz) & whz < -2 ~ "Wasted",
      !is.na(whz)            ~ "Normal",
      TRUE                   ~ NA_character_
    ),
    underweight = case_when(
      !is.na(waz) & waz < -3 ~ "Severely underweight",
      !is.na(waz) & waz < -2 ~ "Underweight",
      !is.na(waz)            ~ "Normal",
      TRUE                   ~ NA_character_
    ),
    any_malnutrition = ifelse(
      ( !is.na(haz) & haz < -2 ) |
      ( !is.na(whz) & whz < -2 ) |
      ( !is.na(waz) & waz < -2 ),
      TRUE, FALSE
    )
  )

# View results
print(df_classified)

```

